Progress Report on the ``Adult Database'' Analysis

### 2009-11-12 report/paper.tex
added more references.

The algorithms we will be using are: ID3, C4.5, CN2 and AQ. Depending on our progress
we will experiment with neural networks and genetic algorithms, which are other
mechanisms for building classifiers.

@@

>>>>

The algorithms we will be using are: ID3 \cite{1}, C4.5 \cite{5}, CN2 \cite{1} and AQ \cite{1}. Depending on our progress
we will experiment with neural networks and genetic algorithms, which are other
mechanisms for building classifiers.

@@

Taking into account the previous analysis of the data, we're now capable of
applying a structured data mining process in order to address the classification
problem posed by the dataset. The final report hopes to compare the performance
and efficiency of different classification algorithms applied to this dataset.
A tentative title for the paper to be delivered as the final report is 
``A comparison of classification algorithms applied to the Adult Database''.
